Survival Analysis

### 2014-04-28 paper.Rnw
Add bfeed education and some analysis

>>>>

One question we may ask is ``Do college-educated women breastfeed longer?'' Intuitively, we may reason that college-educated women are more aware of parenting issues and have more access to parenting resources, so they are more likely to know to breastfeed for a long duration and have the support to breastfeed for a long duration. Or perhaps it is the reverse since less-educated women may depend more on parents for parenting support and their parents may provide more support for breastfeeding long durations.

<<bfeed-education, echo = FALSE, fig = TRUE, include = FALSE>>=
ggsurv(survfit(Surv(duration, delta) ~ yschool > 12, data = bfeed.short)) +
  ggtitle('Breast Feeding Duration by Education') +
  xlab('Duration in Weeks') +
  ylab('Survival') +
  geom_vline(aes(xintercept = 27),
    colour = 'red',
    linetype = 'longdash')
@

The red line represents the survival rate for women with a high school diploma or less and the blue line represents the survival rate for women with some college education.

In this instance, women with some college education tend to breastfeed children longer than women with a high school education or less. That is \emph{not} to say \emph{every} woman with a high school diploma or less breast feeds less than \emph{every} woman with some college education. Nor can we say that having some college education causes longer breastfeeding durations.

% TODO test

\begin{figure}[h]
\begin{center}
\includegraphics[keepaspectratio=true, width=3in]{paper-bfeed-education.pdf}
\end{center}
\caption{Breast Feeding Survival By Education}
\label{fig:bfeed-education}
\end{figure}
